\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 coqimpl.tex

Override Field add := (-).@\YZ{'add' is not a good choice of name---it doesn't make sense to override add with subtraction.}@

Inherits Until MonotonicF.
Override Family MonotonicF.
  Final Field f : nat@\YZ{nat -> nat ?}@ := (+ 1).
  Field p : monotonic f := ...
SealFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \caption{Example Code for Inheritance and Reasoning}\label{fig:plugin-example3}
\end{figure}

>>>>

Override Field bop := (-).@\YZ{'add' is not a good choice of name---it doesn't make sense to override add with subtraction.}\EDJreply{Changed to b(inary)op now}@

Inherits Until MonotonicF.
Override Family MonotonicF.
  Final Field f : nat -> nat@\YZ{nat -> nat ?}\EDJreply{Yes. Thanks}@ := (+ 1).
  Field p : monotonic f := ...
 EndFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \caption{Example Code for Inheritance and Reasoning}\label{fig:plugin-example3}
\end{figure}
